Cover Letter

### 2023-10-23 manuscript.qmd
Update

In this review, we only included randomized controlled trials (RCTs) for the meta-analysis. A major issue of observational evidence is that it is known to have limited internal validity as it is subject to both bias and confounding, therefore observational studies were excluded to ensure reliability of the results by minimizing the risk of bias due to unmeasured confounders. Overall, observational study designs are not the most appropriate to assess the causal relationship between an intervention and an outcome as several characteristics might differ or might change over time between the different intervention groups. So, the inclusion of observational studies in a meta-analysis might introduce bias in the summary effect. Potential biases are likely to be greater for observational studies compared with randomized trials when evaluating the effects of interventions. Observational studies of interventions vary in their ability to estimate a causal effect. Biases affecting observational studies of interventions vary depending on the features of the studies. Published reviews @mao2015 that included observational studies have failed to address potential confounders and the likelihood of increased heterogeneity resulting from residual confounding and from other biases that vary across studies.

Our strategy aimed to study the effectiveness of corticosteroids for HELLP syndrome regarding critical maternal and perinatal outcomes rather than surrogate outcomes. While surrogate outcome measures, such as laboratory results, may provide insights into how a treatment might work, yet they do not necessarily reflect clinical benefits relevant to decision making. Moreover, some interventions that reduce the risk for a surrogate outcome may have no or harmful effects on clinically relevant outcomes, and other interventions having no effect on surrogate measures may improve clinical outcomes @Bucher2015; @cochrane2023ch3. As such, and despite their potential appeal, superiority on a surrogate end point, for example the change in platelet count and liver enzymes, may not reflect actual benefits that corticosteroids have on critical outcomes of women with HELLP syndrome. Furthermore, surrogate end points are potentially misleading and should be avoided, or at least interpreted with caution, as decision makers are required to extrapolate the findings to estimate true patient benefits, resulting in uncertainty about the effect of corticosteroids in HELLP syndrome. Published synthesized evidence @mao2015 that included surrogate outcomes without downgrading the certainty of evidence for indirectness would provide misleading implications for practice. It may not be justifiable or acceptable to use surrogate outcomes for a review when validated or evaluated true endpoints are available @tufanaru2016.

We also focused on studies that compared corticosteroids to placebo or standard care. Various types of corticosteroids differ in their relative potency and duration of action. It would, therefore, be counter-intuitive, and not clinically useful, to compare one corticosteroid to another when evidence fails to show a difference between any corticosteroid vs placebo or no treatment. Investigators @basaran2012 raised serious concerns regarding the credibility of the subgroup analysis results of the Cochrane Review @Woudstra2010 and the application of these subgroup results into clinical practice.

>>>>

In this review, we only included randomized trials for the meta-analysis. A major issue of observational evidence is that it is known to have limited internal validity as it is subject to both bias and confounding, therefore observational studies were excluded to ensure reliability of the results by minimizing the risk of bias due to unmeasured confounders. Overall, observational study designs are not the most appropriate to assess the causal relationship between an intervention and an outcome as several characteristics might differ or might change over time between the different intervention groups. So, the inclusion of observational studies in a meta-analysis might introduce bias in the summary effect. Potential biases are likely to be greater for observational studies compared with randomized trials when evaluating the effects of interventions. Observational studies of interventions vary in their ability to estimate a causal effect. Biases affecting observational studies of interventions vary depending on the features of the studies. Published reviews @mao2015 that included observational studies have not adequately addressed potential confounders and the likelihood of increased heterogeneity resulting from residual confounding and from other biases that vary across studies.

Our strategy aimed to study the effectiveness of corticosteroids in HELLP syndrome for improving critical maternal and perinatal outcomes rather than surrogate outcomes. While surrogate outcome measures, such as platelet count and liver enzymes laboratory results, may provide insights into how a treatment might work, yet they do not necessarily reflect clinical benefits relevant to decision making. Some interventions that reduce the risk for a surrogate outcome may have no or harmful effects on clinically relevant outcomes, and other interventions having no effect on surrogate measures may improve clinical outcomes [@Bucher2015; @cochrane2023ch3]. As such, and despite their potential appeal, superiority on a surrogate end point, for example the change in platelet count and liver enzymes, may not reflect actual benefits that corticosteroids have on critical outcomes of women with HELLP syndrome. Furthermore, surrogate end points are potentially misleading and should be avoided, or at least interpreted with caution, as decision makers are required to extrapolate the findings to estimate true patient benefits, resulting in uncertainty about the effect of corticosteroids in HELLP syndrome. Published synthesized evidence @mao2015 that included surrogate outcomes without downgrading the certainty of evidence for indirectness would provide misleading implications for practice. In the presence of patient relevant outcomes, the use of surrogate outcomes in a synthesis of evidence to inform practice can not be justified @tufanaru2016.

We focused on studies that compared corticosteroids to placebo or standard care. Various types of corticosteroids differ in their relative potency and duration of action. It would, therefore, be counter-intuitive, and not clinically useful, to compare one corticosteroid to another when evidence fails to show a difference between any corticosteroid vs placebo or no treatment. Investigators @basaran2012 raised serious concerns regarding the credibility of the subgroup analysis results of the Cochrane Review @Woudstra2010 and the application of these subgroup results into clinical practice.
